Project-II by Group Sydney

### 2015-12-21 Projet II/report/paper.tex
Add predictions

\begin{abstract}
This report provides a summary of the project two of the PCML class. The project consists of doing binary and multi-class classification on the same set of images. For both methods, we have observed that the given CNN features were more accurate than the HOG one. In binary classification, all methods were approximately equivalent except the Adaboosting and the SVM one. For the multi-class classification, neural networks and SVM were the best methods.

@@

Our final model will be the Adaboosting one, because we considered it has the smallest error, even if there are some outliers, those are still lower than others methods in general.

@@

Our final model is neutal networks and not SVM. Their error is nearly the same, however, the variance of the neural networks is much lower than the one of SVM. Even if both have one outlier and surely have the same stability.

@@

We have seen that advanced machine learning methods are efficient to solve image classification problems. The errors obtained with binary classification and multi-class classification are closed and prove that the nature of the problem is similar. We have tried different methods and have remarked that the neural networks and the SVM models were better than the other in general. In both case, both produces good results. We really think that there is a way of improving SVM model by changing the kernel function because data are surely not separate linearly. At the end, we think that the best way of improving our binary and multi-class classifier would be to find a way to combine the HOG features with the CNN ones.

@@

@misc{DymolaWeb,
  title = "xxx Website",
  author = "xxx",
  howpublished = "\url{http://www.xxx.com}",
  year = "cited July 2008"
}

@misc{IMM2012-06284,
    author       = "R. B. Palm",
    title        = "Prediction as a candidate for learning deep hierarchical models of data",
    year         = "2012",
}

@misc{PMT,
   author = {Piotr Doll\'ar}, 
   title = {{P}iotr's {C}omputer {V}ision {M}atlab {T}oolbox ({PMT})}, 
   howpublished = {\url{http://vision.ucsd.edu/~pdollar/toolbox/doc/index.html}} 
}

>>>>

\begin{abstract}
This report provides a summary of the project two of the PCML class. The project consists of doing binary and multi-class classification on the same set of images. For both methods, we have observed that the given CNN features were more accurate than the HOG one. In binary classification, all methods were approximately equivalent except the Adaboosting and the SVM one, but we choose the SVM method as our final model. For the multi-class classification, neural networks and SVM were the best methods but neural networks has less variance in this case and is considered as our final model. The best way of improving our models would be to find a way to combine HOG features with the CNN one.

@@

Our final model will be the SVM one, because we considered it has one of the smallest error, but it doesn't have any outliers and is more stable than the Adaboosting.

@@

Our final model is neural networks and not SVM. Their error is nearly the same, however, the variance of the neural networks is much lower than the one of SVM. Even if both have one outlier and surely have the same stability.

@@

We have seen that advanced machine learning methods are efficient to solve image classification problems. The errors obtained with binary classification and multi-class classification are closed and prove that the nature of the problem is similar. We have tried different methods and have remarked that SVM model was better than the other in general. In both case, it produces good results and has a small variance. We really think that there is a way of improving it by changing the kernel function because data are surely not separate linearly. At the end, we think that the best way of improving our binary and multi-class classifier would be to find a way to combine the HOG features with the CNN ones.

@@

[1]    IMM2012-06284, R. B. Palm, Prediction as a candidate for learning deep hierarchical models of data, 2012.

[2]   Piotr Doll\'ar, {P}iotr's {C}omputer {V}ision {M}atlab {T}oolbox ({PMT}), \url{http://vision.ucsd.edu/~pdollar/toolbox/doc/index.html}.
